{\color{MsBlue} \subsection{\sihao \kaishu \quad \ \bfseries（三）其他需要说明的情况 
\xiaosihao \fontspec{Times New Roman} Other issues need to be addressed.}}
%

{\sihao \color{MsBlue} \kaishu 1.申请人同年申请不同类型的国家自然科学基金项目情况（
列明同年申请的其他项目的项目类型、项目名称信息，并说明与本项目之间的区别与联系）。}

{\color{MsBlue} \xiaosihao \fontspec{Times New Roman} 
The applications of the applicant for different types of NSFC programs in the 
ame year (please list the types of programs and title of proposals submitted 
in the same year, and explain the difference and connection with this proposal).}

% 无。

{\sihao \color{MsBlue} \kaishu 2.申请人是否存在同年申请或者参与申请国家自然科
学基金项目的单位不一致的情况（如存在上述情况，列明所涉及人员的姓名，申请或参与申请的其他
项目的项目类型、项目名称、单位名称、上述人员在该项目中是申请人还是参与者，并说明单位不一
致原因）。}

{\color{MsBlue} \xiaosihao \fontspec{Times New Roman} 
Whether the applicant's host institution is inconsistent with the one indicated 
in other proposals that he or she submits or participates in applying in the 
same year (if there is any such inconsistency, please list the names of the 
personnel involved, the types of programs, titles of proposals, names of host 
institutions for other projects that you applied or participated in, whether 
the abovementioned personnel are the applicants or participants in the projects, 
and explain the reasons for the inconsistency).}

% 无。

{\sihao \color{MsBlue} \kaishu 3.申请人是否存在与正在承担的国家自然科学基金项目的单位
不一致的情况（如存在上述情况，列明所涉及人员的姓名，正在承担项目的批准号、项目类型、
项目名称、单位名称、起止年月，并说明单位不一致原因）。}

{\color{MsBlue} \xiaosihao \fontspec{Times New Roman} 
Whether the applicant's host institution is inconsistent with the one indicated 
in the NSFC project that he/she is undertaking (if there is any such inconsisten
cy, please list the name of the personnel involved, approval number, type of pro
gram, title of proposal, name of host institution, start and end dates of the un
dertaking project, and explain the reasons for the inconsistency).}

% 无。

{\sihao \color{MsBlue} \kaishu 4.申请人教育或工作经历若不连续请说明原因。}

{\color{MsBlue} \xiaosihao \fontspec{Times New Roman} 
If there is any discontinuity in education or work experience, please explain 
the reason.}

{\sihao \color{MsBlue} \kaishu 5. 其他。 
\xiaosihao \fontspec{Times New Roman} Others.}


% 无。
